\Large \bf One-Step, Three-Factor Authentication With Custom-Fit, In-Ear EEG

### 2017-02-14 paper.tex
New figures, some proofs

\begin{table*}[t]
\centering
%% \begin{tabular}{llllll}
\begin{tabularx}{\textwidth}{llllll}
Task & Description & Stimuli? & Secret? & Eyes & Imagery\\
\hline
Breathe & Relaxed breathing with eyes closed & No & No & Closed & None\\
Breathe - Open & Relaxed breathing with eyes open & No & No & Open & None\\
Sport & Sport-related motor imagery & No & Yes & Closed & Motor\\
Song & Imagining hearing a song & No & Yes & Closed & Aural\\
Song - Open & Song task, with eyes open & No & Yes & Open & Aural\\
Speech & Imagining a spoken phrase & No & Yes & Closed & Aural\\
Listen & Listening to noise modulated at 40 Hz & Yes & No & Closed & None\\
Face & Imagine a person's face & No & Yes & Closed & Visual\\
Sequence & Imagine face, a number, and word on timed cues & Yes & Yes & Open & Visual\\
\hline
\end{tabularx}
\caption{Properties of authentication tasks. We selected tasks with a variety of different properties, but preferred tasks that did not require external stimuli, as the need to present such stimuli at authentication time could present challenges for usability and user security.}
\label{tab:tasks}%
\end{table*}

@@

Breathe appeared as the best task across all participants. Given our training strategy, these results indicate that a given person's breathe task is distinguishable not only among other tasks, but among breathe tasks from other participants.
All best-performing tasks in our set achieved perfect FAR and FRRs, with the exception of P5, whose best-performing task (breathe) had a nonzero FRR.

@@

\begin{table}[h]
\begin{center}
\begin{tabular}{lrrr}
 & Original & Within-tasks & Within-participants\\
\hline
FAR & 0.000074 & 0.000724 & 0.00252\\
FRR & 0.00442 & 0.001522 & 0.0397\\
\end{tabular}
\end{center}
\caption{Mean FAR and FRR for all participants and passthoughts across three different training strategies.}
\label{tab:compare}
\end{table}

>>>>

\begin{table*}[t]
\centering
%% \begin{tabular}{llllll}
\begin{tabularx}{\textwidth}{llllll}
Task & Description & Stimuli? & Secret? & Eyes & Imagery\\
\hline
Breathe & Relaxed breathing with eyes closed & No & No & Closed & None\\
Breathe - Open & Relaxed breathing with eyes open & No & No & Open & None\\
Sport & Imagine acting out a sport-related task & No & Yes & Closed & Motor\\
Song & Imagine hearing a song & No & Yes & Closed & Aural\\
Song - Open & Song task, with eyes open & No & Yes & Open & Aural\\
Speech & Imagine a spoken phrase & No & Yes & Closed & Aural\\
Listen & Listen to noise modulated at 40 Hz & Yes & No & Closed & None\\
Face & Imagine a person's face & No & Yes & Closed & Visual\\
Sequence & Imagine face, a number, and word on timed cues & Yes & Yes & Open & Visual\\
\hline
\end{tabularx}
\caption{Properties of authentication tasks. We selected tasks with a variety of different properties, but preferred tasks that did not require external stimuli, as the need to present such stimuli at authentication time could present challenges for usability and user security.}
\label{tab:tasks}%
\end{table*}

@@

All best-performing tasks in our best-case set achieved perfect FAR and FRRs, with the exception of P5, whose best-performing task (breathe) had a nonzero FRR.
Breathe appeared as the best task across all participants. Given our training strategy, these results indicate that a given person's breathe task is distinguishable not only among other tasks, but among breathe tasks from other participants.
This task performed about as well as its open-eyes counterpart (Figure \ref{fig:meanByTask}), as did /Song (eyes open)/ and /sport/ (though, interestingly, song with eyes closed performed less well).

\begin{figure}[htbp]
\centering
\includegraphics[width=.9\linewidth]{./figures/mean-far-by-task.png}
\caption{FAR in the left ear by task, across all subjects.}
\label{fig:meanByTask}
\end{figure}

@@

\begin{table}[h]
\begin{center}
\begin{tabular}{lrrr}
 & Original & Within-tasks & Within-participants\\
\hline
FAR & 0.000074 & 0.000724 & 0.002523\\
FRR & 0.004424 & 0.001522 & 0.039702\\
\end{tabular}
\end{center}
\caption{Mean FAR and FRR for all participants and passthoughts across three different training strategies.}
\label{tab:compare}
\end{table}
